
## Overview

"fringe: un dataset adornado"

homodatum helps to manage dataframes in a more human way. This package mainly adds information to data (metadata) by creating new classes for values (hdTypes) and dataframes (hdFringe)

The main function of this package is `makeup()`. It takes a date, number o character value and returns it into a human readable format


## Installation

Install the development version of makeup from GitHub with:

``` r
# install.packages("devtools")
remotes::install_github("datasketch/makeup")
```

## Example

This is a basic example which shows you how this packages work:

Let´s load `makeup` package

```{r library}
library(makeup)
library(dstools)
```

### Making _number_ values human readable

```{r num example}
x <- c(1234.56, 432141, 0.12)

makeup(x, 
       sample = "1,432.1")
```

### Making _character_ values human readable

```{r chr example}
x <- c("hello", "WoRlD","Hello world")

makeup(x, sample = "down")

makeup(x, sample = "UPPER")

makeup(x, sample = "Title phrase")

makeup(x, sample = "Title Case")
```

### Making _date_ values human readable

```{r date example}
x <- as.Date(c("2020-03-05","2020-06-20"))

makeup(x)
```

Learn about the many ways to work with formatting dates values in `vignette("working-with-dates")`
